\documentclass[]{article}

%opening
\title{An annotated bibliography of the  scientific publication of William Robert Breckon Lionheart}
\author{William RB Lionheart}

\begin{document}

\maketitle


\section{Brief biography}
Lionheart is an applied mathematician born in 1962 in Oxford. His birth name was William Robert Breckon and is known as Bill. He and his wife changed their surname to Lionheart after they married, an allusion to his wife's mothers maiden name Lion (Norman Irish De Leon).  He gained a BSc (1st class honours) in Mathematics from Warwick University in 1983, studied dynamical systems ad differential Geometry as a Harkness Fellow at University of California Berkeley 1983-1985 where he passed the candidacy exam for a PhD. He started a Phd in Electrical Impedance Tomography in 1985 at Oxford Polytechnic which he finished in 1990, having been appointed a lecturer there in 1987.  He left what had become Oxford Brookes University in 1999 as a senior lecturer where he moved to UMIST. He was a Reader then Professor of Applied Mathematics at UMIST, which became The University of Manchester where he works to date.

\section{Electrical Impedance Tomography}

Lionheart's PhD thesis was in ``Image Reconstruction in Electrical Impedance Tomography''\cite{breckon1990image}, under the supervision of Michael Pidcock. His external supervisor was David Barber at Sheffield University. He worked on practical but mathematically sound reconstruction algorithms with an emphasis on biomedical application. Early contributions included \cite{breckon1988ill} \cite{breckon1988progress} \cite{breckon1988data}.


\section{Magnetic induction tomography and metal detection}

\section{Absorption tomography}

\section{Tensor tomography}

\section{Polarized neutron tomography}

\section{Polarized light tomography}

\section{Navigation and geometry}

\section{Data sets}

\section{Popular articles and public communications of science}

\section{Obituaries}

\section*{Copyright}
This document is published under Creative Commons Attribution 4.0 International (CC BY 4.0) licence. It is copyright \textcopyright William Robert Breckon Lionheart.

\bibliography{mypubls}{}
\bibliographystyle{plain}
\end{document}
